\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

%-------------------------------------------
% HEADER / FOOTER SETTINGS
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-------------------------------------------
% MARGINS
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------------------------------
% SECTION FORMATTING
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is ATS parsable
\pdfgentounicode=1

%-------------------------------------------
% CUSTOM COMMANDS
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Matthew Chin} \\ \vspace{1pt}
    \small 781-697-4238 $|$ \href{mailto:matthwchin@proton.me}{\underline{matthwchin@proton.me}} $|$ 
    \href{https://linkedin.com/in/matthewleechin}{\underline{linkedin.com/in/matthewleechin}} $|$
    \href{https://github.com/balnc9}{\underline{github.com/balnc9}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland}{College Park, MD}
      {Bachelor of Science in Computer Science, Minor in Business}{Jan. 2024 -- May 2027}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Undergraduate Data Research Assistant}{Feb. 2025 -- Present}
      {Digital Media Lab, UMD}{College Park, MD}
      \resumeItemListStart
        \resumeItem{Build Chrome Extension + Next.js frontend to scrape and visualize live news metadata, using Chart.js, TypeScript, and DOM parsing}
        \resumeItem{Designed interactive dashboards and visualizations plotting engagement metrics, enabling researchers and local news anchors to analyze user interaction patterns}
        \resumeItem{Implemented live data pipelines for journalism platforms (e.g., Baltimore Banner), improving efficiency of content analysis}
      \resumeItemListEnd

    \resumeSubheading
      {Development Intern}{Jun. 2025 -- Present}
      {Colexia}{New York, NY}
      \resumeItemListStart
        \resumeItem{Built Python + BeautifulSoup4 scrapers to index/organize product datasets, improving dataset standardization for external ML models}
        \resumeItem{Contributed to Firebase-based wait list website to support early-stage startup growth and exposure}
        \resumeItem{Automated product ingestion pipeline into xlsx folders using Google Drive API, accelerating data reports by 70\% }
      \resumeItemListEnd

    \resumeSubheading
      {Helpdesk IT Technician}{Aug 2020 -- May 2023}
      {Stone Rehabilitation \& Senior Living}{Newton Upper Falls, MA}
      \resumeItemListStart
        \resumeItem{Shadowed and co-delivered Tier 1/2 helpdesk support for 200+ staff, resolving hardware, software, and networking issues.}
        \resumeItem{Configured and maintained workstations, printers, internal system hardware, reducing downtime and ensuring HIPAA compliance.}
        \resumeItem{Trained staff on new systems and provided on-call technical support, creating a reliable, user-friendly IT environment}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Pseudo Random Number Generation Lab} $|$ \emph{Linux (Ubuntu), C, Cryptography}}{}
      \resumeItemListStart
        \resumeItem{Investigated weaknesses in pseudo-random number generation within cryptographic systems.}
        \resumeItem{Implemented key-generation algorithms in C, highlighting predictable patterns exploitable in AES encryption.}
        \resumeItem{Compared /dev/random vs. /dev/urandom, analyzing entropy, blocking, and randomness quality.}
        \resumeItem{Conducted entropy analysis of kernel randomness sources (keyboard, disk I/O, interrupts).}
        \resumeItem{Applied statistical tools (ent) to assess randomness, strengthening 128/256-bit key generation methods.}
      \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{Temperature Time Machine} $|$ \emph{Python, Data Science}}{}
      \resumeItemListStart
        \resumeItem{Built a pipeline analyzing 57,000+ records over 155 years of NOAA/NASA climate data.}
        \resumeItem{Applied multivariate regression, Fourier Transform, and statistical tests to identify climate patterns.}
        \resumeItem{Automated data ingestion and error handling, outputting animated time-series visualizations.}
        \resumeItem{Produced publication-grade statistical reports demonstrating long-term warming cycles.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Smart Story Agent} $|$ \emph{Next.js, TypeScript, AI}}{}
      \resumeItemListStart
        \resumeItem{Developed a full-stack web app analyzing live news articles with Claude API + custom algorithms for engagement metrics.}
        \resumeItem{Designed interactive UI with Tailwind CSS + Framer Motion, increasing usabiity and visualization quality.}
        \resumeItem{Integrated PostHog analytics for user behavior tracking and engagement insights.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{VFC Community App} $|$ \emph{Next.js, TypeScript, AI}}{}
      \resumeItemListStart
        \resumeItem{Contributed to a cross-platform serving 250+ users, building event management, push notifications, and MFA authentication.}
        \resumeItem{Built reusable component library + custom hooks that reduced code duplication by 40\%}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{Baltimore Banner Scraper} $|$ \emph{JavaScript, HTML, CSS, Chart.js}}{}
      \resumeItemListStart
        \resumeItem{Engineered a Chrome Extension (Manifest v3) to scrape article metadata (word count, images, headers) and visualize results in real time.}
        \resumeItem{Leveraged Web Storage + DOM parsing for efficient data restructuring and UI rendering}
      \resumeItemListEnd

      
    \resumeProjectHeading
        {\textbf{Minesweeper Game Clone} $|$ \emph{C++}}{}
      \resumeItemListStart
        \resumeItem{Designed randomized mine placement algorithms with adaptive board sizes and difficulty levels.}
        \resumeItem{Implemented a dynamic UI with color-coded indicators for mine proximity.}
        \resumeItem{Optimized memory management for large board states and recursive operations.}
      \resumeItemListEnd
      
    

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Java, Python, C , (Rust, OCaml, C++)} \\
      \textbf{Frameworks}{: React, Next.js, React Native, Firebase, Tailwind, Chart.js} \\
      \textbf{Developer Tools}{: Git, PostHog, Framer Motion, BeautifulSoup4, Chrome Extensions API, Claude API} \\
      \textbf{Data}{: Pandas, NumPy, MATLAB, SciPy, Statsmodels}\\
      \textbf{Certifications}{: Tata Cybersecurity Job Simulation, Mastercard Cybersecurity Job Simulation, AWS ML Solutions (Coursera), CompTIA Sec+ (in progress), SEEDLabs PRNG Lab (Ubuntu Linux VM 20.4)}\\
      \textbf{Other}{: Seal of Bi-literacy (Spanish \& English, 2022)}\\
      \textbf{Coursework}{: Cryptography, Data Structures \& Algorithms, Organization of Programming Languages, Computer Systems (C), OOP I/II, Discrete Structures, Linear Algebra, Applied Statistics}
    }}
  \end{itemize}

%-------------------------------------------
\end{document}
